Restrictive Clearance Comparison

### 2025-02-11 data-raw/RestrictiveClearance_comparison.Rmd
Included pka into ctxR data loading. Also loaded RData for binding affinity.

@@

```{r lipinksi_test_data}
target_chem_info <- get_chemical_details_batch(DTXSID = target_chems,
                                               rate_limit = 1L)
target_chem_properties <- get_chem_info_batch(DTXSID = target_chems, 
                                              rate_limit = 1L) %>%
  filter(name == "LogKow: Octanol-Water") %>% distinct()

target_chem_properties %>%
  ggplot(aes(x = source, y = value)) +
  geom_point() +
  geom_line(aes(group = dtxsid), color = "grey10", alpha = 0.1) +
  geom_hline(yintercept = 5, linetype = "longdash") +
  facet_grid(cols = vars(propType), scales = "free_x") +
  theme_bw() +
  theme(axis.text.x = element_text(hjust = 1, angle = 45))

@@

@@

py_h_donors = [Chem.Descriptors.NOCount(x) for x in mol_from_smiles]
py_h_acceptors = [Chem.Descriptors.NHOHCount(x) for x in mol_from_smiles]
```

>>>>

```{r load_Kd}
load(paste0(Sys.getenv("OD_DIR"),
            "Profile/Documents/New-HTTK-raw-2019-05-06.RData")
)
```

@@

```{r lipinksi_test_data}
target_chem_info <- get_chemical_details_batch(DTXSID = target_chems,
                                               rate_limit = 1L)
target_chem_properties <- get_chem_info_batch(DTXSID = target_chems, 
                                              rate_limit = 1L) %>%
  filter(name %in% c("LogKow: Octanol-Water",
                     "pKa Acidic Apparent",
                     "pKa Basic Apparent")) %>% distinct()

target_chem_properties %>%
  ggplot(aes(x = source, y = value)) +
  geom_violin() +
  geom_line(aes(group = dtxsid), color = "grey10", alpha = 0.1) +
  geom_hline(yintercept = 5, linetype = "longdash") +
  facet_grid(cols = vars(propType), scales = "free_x",
             rows = vars(name)) +
  scale_y_log10() +
  theme_bw() +
  theme(axis.text.x = element_text(hjust = 1, angle = 45))

@@

target_chem_pw_predicted <- target_chem_properties %>%
  filter(source == "ACD/Labs") %>%
  distinct(propertyId, value, dtxsid) %>%
  pivot_wider(names_from = propertyId,
              values_from = value)

@@

py_h_donors = [Chem.Descriptors.NOCount(x) for x in mol_from_smiles]
py_h_acceptors = [Chem.Descriptors.NHOHCount(x) for x in mol_from_smiles]
py_tpsa = [Chem.Descriptors.TPSA(x) for x in mol_from_smiles]
```
